---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Numpute

<!-- badges: start -->
<!-- badges: end -->

The goal of CatCorr is to evaluate factor variables for correlation, a task which is somewhat challenging given that traditional correlation calculations are intended primarily for numeric variables.

## Installation

You can install the development version of CatCorr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("easoneli176/CatCorr")
```

## Example

First, the crmv function takes 2 factor variables in the form of vectors and calculates their Cramer's V, which is the metric we use to approximate correlation for factor variables throughout this package.

```{r example}
library(CatCorr)

mock_data<-data.frame(fac1 = c(rep("A",3),rep("B",3),rep("C",3),rep("D",3)) , fac2 = c(rep("E",3),rep("F",2),rep("G",4),rep("H",3)))

crmv(mock_data[,1],mock_data[,2])
```

Taking this a step further, the onevarcv function takes one variable in a dataframe and calculates its Cramer's V with all other variables in that dataframe.

```{r example2}
mock_data$fac3<-c(rep("I",4),rep("J",4),rep("K",4))

onevarcv(mock_data[,1],mock_data)
```

Continuing onward, the crmvtbl function calculates the Cramer's V for all variables in a dataframe.

```{r example3}
crmvtbl(mock_data)
```

Next, crmvtbl_condense is a helper function that takes a dataframe and makes a new table compatible to be fed to catcorrplot

```{r example4}
crmvtbl_condense(mock_data)
```

Finally, the catcorrplot function brings all these together and makes a nice visualization for all the correlations between the factor values in the dataframe.

```{r example5}
catcorrplot(mock_data)
```
